AA Distributed Software Development Methodology

### 2013-06-02 paper.tex
paragrafo penalvim integrado

All AA reports made by the developers are ultimatelly sent to a Web server and
become publically aggregated on a Website. It is then possible for a manager or another
developer to follow very closely the work of a given developer, nearly real-time,
reading each of his small reports or micrologs of what he is working on.

@@

After the initial training period of 1 month, the initiated ``Macambiras''
worked during 6 additional months on a large range of free software projects,
divided into work groups --- each work group focusing on a specific theme like
video, audio and web --- and funded by contracts, freelance, and support of the
Pont\~{a}o N\'{o}s Digitais\footnote{\url{http://nosdigitais.teia.org.br}}.
Table~\ref{tabela:criados} has a list of \emph{new} free software applications
created by ``Lab Macambira'' since July 2011.

>>>>

All AA reports made by the developers are ultimatelly sent to a Web server and
become publically aggregated on a Website called pAAnel. It is then possible for a manager or another
developer to follow very closely the work of a given developer, nearly real-time,
reading each of his small reports or micrologs of what he is working on.

@@

After the initial training period of 1 month, the initiated `Macambiras'
worked during 6 additional months on a large range of free software projects,
divided into work groups --- each work group focusing on a specific theme like
video, audio and web --- and funded by contracts, freelance, and support of the
Pont\~{a}o N\'{o}s Digitais\footnote{\url{http://nosdigitais.teia.org.br}}.
Table~\ref{tabela:criados} has a list of \emph{new} free software applications
created by `Lab Macambira' since July 2011.

While using the AA system, developers learned to work asynchronously with others
and got used to the habit of periodically updating their status on their
projects. Each programmer was given the chance to work with considerable
freedom, in any place and time of preference. The strictest required
responsibility was that of using AA for at least one sesssion of 2h per day,
while working on the agreed upon tasks.  The online pAAnel allowed each
developer to quickly grasp activities from others while avoiding interrupting them, a
process further aided by the screencasts. Adjustments to the task deadlines and
milestones (which were managed in Trac) were done based on verified progress of
individuals and labMacambira.sf.net team as a whole. The various newcommers
benefitted from a fast learning team by the use of AA as a flexible and simple
transparency system. Updates from the team were not transmitted on a
person-to-person basis, but rather on a person-to-team basis based on the
available online progress information.
